Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-07 introductory.tex
working on the case study section

\section{Case Study}
\label{sec:case}

%\todo{Either leave as is or add more info on usage by college if possible}
\subsection*{Case Study: The API (Zeeguu)}
\label{sec:api}

  \zee\footnote{\url{https://github.com/zeeguu-ecosystem/}} is a platform and an ecosystem of applications for accelerating vocabulary acquisition in a foreign language \cite{Lungu16}. 
%
  The architecture of the ecosystem has at its core an API and a series of satellite applications that together offer to a learner three main inter-dependent features:

    \item \textit{Reader applications} that provide effortless translations for those texts which are too difficult for the readers.

    \item \textit{Interactive exercises} that are personally generated based on the preferences and past likes of the learner.

    \item \textit{Article recommendations} which are also personalized for the interests of each learner and come with a difficulty estimation that helps the learner find articles with appropriate difficulty.

  The core API is implemented with Flask and Python provides and correspondingly three types of functionality: contextual translations, personalized exercise suggestions, and article recommendations. In total, the API provides a bit under 50 endpoints, out of which around a dozen are very frequently used. 
  % The development of the core API itself is a research project. 
  %
  At the time of writing, the ecosystem consists of a reader web application, a web-based exercises platform, and a smartwatch application, which are used by more than \activeUserCount active users on a regular basis. 
  %The majority of the users come from a high school and a language school in the city of Groningen. However, some users are using it on their own, outside of any formal educational context. The highest load we observed until now on the API consisted of 12K requests in a single day.

  \ml{add more numbers that show how impressive is our API}
  \va{I don't think this is necessary - I am also moving the user characteristics in the respective subsection below}

\newpage

\subsection*{Case Study: The Technology (Flask)}
\label{sec:flask}

 \va{Consider this subsection moving before the introduction of Zeeguu; it would make a smoother reading}

 Flask is a microframework for Python. It IS USED BY THOUSANDS OF PROJECTS. ELABORATE MORE ON THIS... 
 %\vspace{2cm}
 \va{Actually, you probably have already introduced Flask in the first section, so you just need the first sentence: As discussed in the previous section, Flask is a microframework for Python.}
%
% Flask depends on two external libraries: the Jinja2 template engine and the Werkzeug WSGI toolkit. 
%
 ``Micro'' does not mean that a whole web application has to fit into a single Python file (although it certainly can), nor does it mean that Flask is lacking in functionality. The ``micro'' in microframework means Flask aims to keep the core simple but extensible. Flask won’t make many decisions for the user, such as what database to use. Those decisions that it does make, such as what templating engine to use, are easy to change. Everything else is up to the user.%, so that Flask can be everything you need and nothing you don’t.

 Flask has many configuration values, with sensible defaults, and a few conventions when getting started. By convention, templates and static files are stored in subdirectories within the application's Python source tree, with the names templates and static respectively. While this can be changed, it usually don’t have to, especially when getting started.
%
 A Python web application based on WSGI has to have one central callable object that implements the actual application. In Flask this is an instance of the Flask class. Each Flask application has to create an instance of this class itself and pass it the name of the module, but why can’t Flask do that itself?
 \va{Do you really need the part in the previous sentence after the comma? Just ref the listing}

@@

@@

The \tool has been deployed with the case study API for 
ten months, time in which more than 112.000 hits of the API have 
been recorded. \va{which ten months?}
The majority of the users come from a high school and a language school in the city of Groningen using \zee to study foreign languages. However, some users are using it on their own, outside of any formal educational context. The highest load we observed until now on the API consisted of 12K requests in a single day. \va{not sure what can be added here; maybe that's enough}

\subsection*{Role of Authors in the Case Study}
\va{not sure what else you would like to add here...}
One of the authors leads the developer team that develops the \zee API.

>>>>

\section{Case Study}

\subsection{The Technology Stack}
\label{sec:flask}

 As discussed in the previous section, Flask is a microframework for Python. ``Micro'' does not mean that a whole web application has to fit into a single Python file (although it certainly can), nor does it mean that Flask is lacking in functionality. The ``micro'' in microframework means Flask aims to keep the core simple but extensible. Flask won’t make many decisions for the user, such as what database to use. Those decisions that it does make, such as what templating engine to use, are easy to change. Everything else is up to the user.

 Flask has many configuration values, with sensible defaults, and a few conventions when getting started. By convention, templates and static files are stored in subdirectories within the application's Python source tree, with the names templates and static respectively. While this can be changed, it usually don’t have to, especially when getting started.
%
 A Python web application based on WSGI has to have one central callable object that implements the actual application. In Flask this is an instance of the Flask class. Each Flask application has to create an instance of this class itself and pass it the name of the module. The following code snippet presents a simple ``Hello World'' web service written in Python with the help of the Flask framework.

@@

%\todo{Either leave as is or add more info on usage by college if possible}
\subsection{An Ecosystem With a Service API at its Core}
\label{sec:api}
\label{sec:case}

  \zee\footnote{\url{https://github.com/zeeguu-ecosystem/}} is a platform and an ecosystem of applications for accelerating vocabulary acquisition in a foreign language \cite{Lungu16}. 
%
  The architecture of the ecosystem has at its core an API and a series of ecosystem applications that together offer to a learner three main inter-dependent features:

    \item \textit{Reader applications} that provide one-click (or one touch, on touch-enabled devices) translations for the words and expressions in a text that the reader does not understand. Besides facilitating reading, the translations serve as input to a user knowledge model that is used further to generate personalized exercises and further reading recommendations.

    \item \textit{Interactive exercises} are generated based on the texts that the reader has studied in the past and are scheduled in such a way as to optimize the memory retention and to prioritize the most important unknown vocabulary items.

    \item \textit{Article recommendations} are also personalized for the interests and language capabilities of each learner. The recommendations come with a difficulty estimation that helps the learner find articles with appropriate difficulty.

  \Fref{fig:zeeguuarch} presents a high-level view of the case study ecosystem.  The core API is implemented with Flask and Python provides and correspondingly three types of functionality: contextual translations, personalized exercise suggestions, and article recommendations. In total, the API provides a bit under 50 endpoints, out of which around a dozen are very frequently used. The development of the core API itself is a research project. One of the is part of the developer team that maintains and evolves the \zee API.

    \begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\linewidth]{zeeguu-architecture}
      \caption{The architecture of the Zeeguu ecosystem}
      \label{fig:zeeguuarch}
    \end{figure}

  At the time of writing, the ecosystem consists of a reader web application, a web-based exercises platform, and a smartwatch application, which are used by more than \activeUserCount active users on a regular basis. The highest load we observed until now on the API consisted of 12K requests in a single day.

@@

The \tool has been deployed with the case study API for 
ten months, time in which more than 112.000 hits of the API have 
been recorded. \va{which ten months?}

The users come from several Dutch highschools and a language center associated with a DutchUniversity. However, some users are using it on their own, outside of any formal educational context. The learners use \zee to study a variety of of foreign languages including German, Dutch, French. They have also diverse native languages, including: Chinese, Dutch, and English.

The highest load we observed until now on the API consisted of 12K requests in a single day. \va{not sure what can be added here; maybe that's enough}

\subsection*{Role of Authors in the Case Study}
\va{not sure what else you would like to add here...}
